---
title: "VUBmd"
author: "Jan Wijffels"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: false
vignette: >
  %\VignetteIndexEntry{VUBmd}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE, cache=FALSE}
options(width = 1000)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, comment = NA, eval = TRUE)
```

## VUBmd

The package allows you to easily create using Rmarkdown

- presentations with the identity of the VUB
- articles with the identity of the VUB

To get started either in RStudio, select the VUB templates (`VUB slides` and `VUB article`) at
`File` > `New file` > `R Markdown` > `From template`. Or just copy-paste the examples to your current working directory and start creating a presentation or an article.

```{r, eval=FALSE}
rmd <- system.file(package = "VUBmd", "rmarkdown", "templates", "vub_slides", "skeleton", "skeleton.Rmd")
file.copy(rmd, "vub-slides.Rmd")
``` 

```{r, eval=FALSE}
rmd <- system.file(package = "VUBmd", "rmarkdown", "templates", "vub_article", "skeleton", "skeleton.Rmd")
file.copy(rmd, "vub-article.Rmd")
```  


